### 2017-01-27 manuscript.rmd
typo

We next examined the possibility that ascertainment biases were differentially impacting the inference of evolution following duplication and speciation events. We focused on two possible sources of bias - node depth and branch length. We found no evidence that either affacted our results (Supplementary materials).

@@

	# Calcualte some summary statistics 
	ortholog_r = 
		pairwise_summary %>% 
		filter( D=="N" ) %>% 
		select( tau_a, tau_b ) %>% 
		cor( ) %>% 
		.[ 1, 2 ]

>>>>

We next examined the possibility that ascertainment biases were differentially impacting the inference of evolution following duplication and speciation events. We focused on two possible sources of bias - node depth and branch length. We found no evidence that either affected our results (Supplementary materials).

@@

	# Calculate some summary statistics 
	ortholog_r = 
		pairwise_summary %>% 
		filter( D=="N" ) %>% 
		select( tau_a, tau_b ) %>% 
		cor( ) %>% 
		.[ 1, 2 ]
